Ms 1

### 2018-06-04 ms1/ms1_display.Rmd
new ms1 analys

@@

approp_counts %>%
  select(year, antibiotic, cpkp) %>%
  spread(year, cpkp)
```

@@

```{r raw_drug_trends}
abx_levels = levels(claims_by_abx$abx)

dummy = data_frame(
  year = rep(c(2011, 2014), 3),
  cpkp = c(0, 1500, 0, 250, 0, 100),
  panel = factor(c(1, 1, 2, 2, 3, 3)),
  abx = 'pde'
)

@@

claims_by_abx %>%
  bind_rows(approp_counts) %>%
  filter(antibiotic != 'n_pde_top10') %>%
  rename(abx=antibiotic) %>%
  mutate(panel = factor(case_when(
    .$abx %in% c('n_pde', 'approp', 'inapp', 'indet') ~ 1,
    .$abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'trimethoprim/sulfamethoxazole', 'levofloxacin') ~ 2,
    .$abx %in% c('amoxicillin/clavulanate', 'doxycycline', 'nitrofurantoin', 'clindamycin') ~ 3
  ))) %>%
  filter(!is.na(panel)) %>% # remove metro
  mutate(abx=case_when(
    .$abx == 'n_pde' ~ 'Overall use',
    .$abx == 'inapp' ~ 'Inappropriate use',
    .$abx == 'approp' ~ 'Appropriate use',
    .$abx == 'indet' ~ 'Indeterminate use',
    .$abx == 'amoxicillin/clavulanate' ~ 'amox/clav',
    .$abx == 'trimethoprim/sulfamethoxazole' ~ 'TMP/SMX',
    TRUE ~ .$abx)
  ) %>%
  arrange(year, desc(cpkp)) %>%
  {
  ggplot(., aes(x=year, y=cpkp, group=abx)) +
  geom_blank(data=dummy) +
  geom_line() +
  geom_text_repel(
    data=filter(., year==2013),
    aes(label=abx)
  ) +
  facet_wrap(~panel, scales='free_y', labeller=labeller(panel=panel_labels)) +
  theme_classic() +
  theme(panel.grid.minor.x=element_blank(),
        strip.background = element_blank(),
        plot.margin=unit(c(1.0, 1.0, 0.5, 0.5), 'lines')) +
  scale_x_continuous(expand=c(0, 0), name='') +
  scale_y_continuous(expand=c(0, 0), name='claims per 1,000 beneficiaries per year')
  }

ggsave('fig/raw_drug.pdf', height=5.0, width=9.0, unit='in')
```

@@

abx_trends %>%
  mutate(antibiotic=case_when(
    .$antibiotic == 'n_abx' ~ 'Overall use',
    .$antibiotic == 'amoxicillin/clavulanate' ~ 'amox/clav',
    .$antibiotic == 'trimethoprim/sulfamethoxazole' ~ 'TMP/SMX',
    TRUE ~ .$antibiotic)
  ) %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('Overall use', 'Inappropriate use', 'Appropriate use', 'Indeterminate use'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_col(fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in claims per beneficiary per year from 2011 to 2015 (%)') +
  scale_y_continuous(limits=c(-20, 30), breaks=c(-20, -10, 0, 10, 20, 30), expand=c(0.0, 0.00)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=12),
        axis.text = element_text(size=12))

ggsave('fig/abx_trends.pdf', width=6.4, height=4.5, units='in')
```

```{r}
app_trends = read_tsv('tables/approp_models.tsv') %>%
  mutate(antibiotic=case_when(
    .$appropriateness == 'inappropriate' ~ 'Inappropriate use',
    .$appropriateness == 'appropriate' ~ 'Appropriate use',
    .$appropriateness == 'indeterminate' ~ 'Indeterminate use')
  ) %>%
  select(-appropriateness) %>%
  format_model()

@@

@@

>>>>

## Top 10 fraction

```{r}
pct_top10 = claims_by_abx %>%
  filter(antibiotic %in% c('n_pde', 'n_pde_top10')) %>%
  select(year, antibiotic, n_pde) %>%
  spread(antibiotic, n_pde) %$%
  { 100 * sum(n_pde_top10) / sum(n_pde) }
```

The top 10 antibiotics accounted for `r round(pct_top10, 2)`% of claims.

@@

approp_counts %>%
  select(year, antibiotic, cpkp) %>%
  spread(year, cpkp) %>%
  kable()
```

@@

```{r raw_drug_trends}
dummy = data_frame(
  year = rep(c(2011, 2014), 3),
  cpkp = c(0, 1500, 0, 250, 0, 100),
  panel = factor(c(1, 1, 2, 2, 3, 3)),
  abx = 'pde'
)

@@

cba_dat = claims_by_abx %>%
  bind_rows(approp_counts) %>%
  filter(antibiotic != 'n_pde_top10') %>%
  rename(abx=antibiotic) %>%
  mutate(panel = factor(case_when(
    .$abx %in% c('n_pde', 'approp', 'inapp', 'indet') ~ 1,
    .$abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'trimethoprim/sulfamethoxazole', 'levofloxacin') ~ 2,
    .$abx %in% c('amoxicillin/clavulanate', 'doxycycline', 'nitrofurantoin', 'clindamycin') ~ 3
  ))) %>%
  filter(!is.na(panel)) %>% # remove metro
  mutate(abx=case_when(
    .$abx == 'n_pde' ~ 'Overall use',
    .$abx == 'inapp' ~ 'Inappropriate use',
    .$abx == 'approp' ~ 'Appropriate use',
    .$abx == 'indet' ~ 'Indeterminate use',
    .$abx == 'amoxicillin/clavulanate' ~ 'amox/clav',
    .$abx == 'trimethoprim/sulfamethoxazole' ~ 'TMP/SMX',
    TRUE ~ .$abx)
  ) %>%
  arrange(year, desc(cpkp))

cba_dat %>%
  {
  ggplot(., aes(x=year, y=cpkp, group=abx)) +
  geom_blank(data=dummy) +
  geom_line() +
  geom_text(
    data=filter(., year==2013),
    aes(label=abx),
    nudge_y=c(50, 50, -35, 35,
              26, -8, 10, 8, -8, -6,
              4, 8, -3, -5),
    nudge_x=c(0, rep(-0.5, 3),
              0, 0, 0, 0, 1.3, 0,
              rep(0, 4))
  ) +
  facet_wrap(~panel, scales='free_y', labeller=labeller(panel=panel_labels)) +
  theme_classic() +
  theme(panel.grid.minor.x=element_blank(),
        strip.background = element_blank(),
        plot.margin=unit(c(1.0, 1.0, 0.5, 0.5), 'lines'),
        axis.text.x=element_text(color='black'),
        axis.text.y=element_text(color='black'),
        text=element_text(color='black')) +
  scale_x_continuous(expand=c(0, 0), name='') +
  scale_y_continuous(expand=c(0, 0), name='claims per 1,000 beneficiaries per year')
  }

ggsave('fig/raw_drug.pdf', height=5.0, width=9.0, unit='in')
ggsave('fig/drug_trends.png', height=5.0, width=9.0, unit='in')
```

@@

abx_trends %>%
  mutate(antibiotic=case_when(
    .$antibiotic == 'n_abx' ~ 'Overall use',
    .$antibiotic == 'amoxicillin/clavulanate' ~ 'amox/clav',
    .$antibiotic == 'trimethoprim/sulfamethoxazole' ~ 'TMP/SMX',
    TRUE ~ .$antibiotic)
  ) %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, 'Overall use')) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_col(fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in claims per beneficiary per year from 2011 to 2015 (%)') +
  scale_y_continuous(limits=c(-20, 30), breaks=c(-20, -10, 0, 10, 20, 30), expand=c(0.0, 0.00)) +
  theme_minimal() +
  theme(axis.title.x=element_text(size=12, color='black', hjust=1),
        axis.text = element_text(size=12, color='black'),
        plot.margin = unit(c(0.1, 0.2, 0.1, 0), 'in'))

ggsave('fig/abx_trends.pdf', width=6.4, height=4.5, units='in')
ggsave('fig/abx_trends.png', width=6.4, height=4.5, units='in')
```

```{r}
app_trends = read_tsv('tables/approp_models.tsv') %>%
  mutate(antibiotic=case_when(
    .$appropriateness == 'inappropriate' ~ 'Inappropriate use',
    .$appropriateness == 'appropriate' ~ 'Appropriate use',
    .$appropriateness == 'indeterminate' ~ 'Indeterminate use',
    .$appropriateness == 'overall3' ~ 'Overall use'
    )
  ) %>%
  select(-appropriateness) %>%
  format_model()

@@

rxdx_models %>%
  format_model() %>%
  select(antibiotic, dx_cat, change, p.value) %>%
  filter(antibiotic %in% c('azithromycin', 'levofloxacin'),
         dx_cat %in% c('pneumonia', 'uri'))

@@

### Use for any

Use of a drug for any respiratory bit.

```{r}
rxdx_table_single %>%
  filter(site=='respiratory') %>%
  group_by(year, antibiotic) %>%
  summarize(cpkp = round(sum(cpkp), 1)) %>%
  spread(year, cpkp) %>%
  kable()
```
